Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-21 cogsci2016/paper.tex
results
intro

@@

	Development of tool use \cite{guerin2013survey}, precursors of tool use: behavior without objects, behavior with one object, interaction of objects.	
	Grounding of representation and planning based on a large amount of experiences. 	
	Seemless progression between the successives phases as overlapping waves. 	
	Ongoing process of upgrading representations.	
	Developmental trajectories.

@@

	Curiosity-driven modelling work, emergence of developmental trajectories.
	\cite{oudeyer_intrinsic_2007} 
	\cite{oudeyer_what_2007}
	\cite{flow}
	\cite{sch}
	\cite{santucci2013}
	\cite{cangelosi2010integration}
	\cite{oudeyer2014evolution}

@@

	Other related work
	\cite{ugur2015}
	\cite{schmerlinggoal}

@@

@@

>>>>

%\usepackage{hyperref}

@@

	\paragraph{}
	Development of tool use: different properties \cite{guerin2013survey} (cite others?). 
	List of some properties: grounding of representation and planning based on a large amount of experiences, ongoing process of upgrading representations (others?).
	In that paper we will focus on one important property in the development of precursors of tool use which is the seemless progression 
	between successives phases of behavior with tools and objects which are called overlapping waves [Siegler]. 
	One behavioral description of the successives phases differentiate three phases \cite{guerin2013survey}.
	In the first phase the babies engage mostly in behavior without objects (babbling), in the second phase their behavior has shifted towards interaction with one object, and then interaction between objects.
	[more details: months, experiments]

	\paragraph{}
	We hypothesize that several mechanisms play a role in the structure of this behavioral progression and in particular 
	1) the intrinsic motivation to explore as a self-regulation of the learning growth of complexity, and 
	2) the structure of the representation used to encode sensorimotor experience.

@@

	\paragraph{}
	We will study aspects of these hypothesis leveraging and extending models of curiosity-driven learning of sensorimotor models to the exploration of given hierarchies of sensorimotor models.
	In such hierarchies, parts of the sensory space (e.g. the position of the hand) can be used as a motor space by another higher-level model to explore other sensory spaces.
	We do not study some other important factors of the development of tool use: the autonomous building and evolution of the hierarchy of models but we consider it given to a learning agent.
	We also do not address the question of the role of social guidance.

	Related work
	Curiosity-driven modelling work, emergence of developmental trajectories.
	\cite{oudeyer_intrinsic_2007} 
	\cite{oudeyer_what_2007}
	\cite{flow}
	\cite{sch}
	\cite{santucci2013}
	\cite{cangelosi2010integration}
	\cite{oudeyer2014evolution}

@@

	Other related work
	\cite{ugur2015}
	\cite{schmerlinggoal}
	\cite{forestier2015}
	\cite{unifying}

@@

	Along with this paper we provide open-source Python code\footnote{Source code and notebooks available as a Github repository at \url{https://github.com/sebastien-forestier/CogSci2016}} 
	with iPython/Jupyter notebooks that explain how to reproduce the experiments and analysis.

@@

			\begin{figure}[t]
				\center
				\input{include/F.tikz}
				\caption{Flat architecture}
				\label{F}					
			\end{figure}
